---
title: "6 country survey dashboard"
format: pdf
editor: visual
---

# Dashboard

## Data preparation

```{r}
library("dashboardr")
library(forcats)
library(tidyverse)
library(highcharter)

GenAIuse_groups = factor(c("Never", "Once a week", "2-4 times per week ", "(Almost) every day", "Several times a day"))

data = read_csv('data_modified_04022026.csv')

data = data %>%
  mutate(GenAI_use = fct_relevel(GenAI_use, 
                                 "Never", "Once a week", "2-4 times per week", 
                                 "(Almost) every day","Several times a day"),
    Q8_trust_publisher = fct_relevel(Q8_trust_publisher, 
                                     "Not important at all", "Of little importance", 
                                     "Of average importance", "Very important"),
    Q8_realism = fct_relevel(Q8_realism, 
                             "Not important at all", "Of little importance", 
                             "Of average importance", "Very important"),
    Q8_misinfo_risk = fct_relevel(Q8_misinfo_risk, 
                                  "Not important at all", "Of little importance", 
                                  "Of average importance", "Very important"),
    Q8_human_in_the_loop = fct_relevel(Q8_human_in_the_loop, 
                                       "Not important at all", "Of little importance", 
                                       "Of average importance", "Very important"),
    Q6_read = fct_relevel(Q6_read, 
                                 "Very unwilling", "Somewhat unwilling", "Neutral", 
                                 "Somewhat willing","Very willing"),
    Q6_share = fct_relevel(Q6_share, 
                                 "Very unwilling", "Somewhat unwilling", "Neutral", 
                                 "Somewhat willing","Very willing"),
    Q6_trust = fct_relevel(Q6_trust, 
                                 "Very unwilling", "Somewhat unwilling", "Neutral", 
                                 "Somewhat willing","Very willing"),
    Q6_talk = fct_relevel(Q6_talk, 
                                 "Very unwilling", "Somewhat unwilling", "Neutral", 
                                 "Somewhat willing","Very willing"),
    Q6_ignore = fct_relevel(Q6_ignore, 
                                 "Very unwilling", "Somewhat unwilling", "Neutral", 
                                 "Somewhat willing","Very willing"),
    Q10_free_companies =fct_relevel(Q10_free_companies, 
                                 "Strongly disagree", "Disagree", 
                                 "Neither agree, nor disagree", 
                                 "Agree","Strongly agree"),
    Q10_government_decides = fct_relevel(Q10_government_decides, 
                                 "Strongly disagree", "Disagree", 
                                 "Neither agree, nor disagree", 
                                 "Agree","Strongly agree"),
    Q10_right_to_complain = fct_relevel(Q10_right_to_complain, 
                                 "Strongly disagree", "Disagree", 
                                 "Neither agree, nor disagree", 
                                 "Agree","Strongly agree"),
    Q10_involve_civil_society = fct_relevel(Q10_involve_civil_society, 
                                 "Strongly disagree", "Disagree", 
                                 "Neither agree, nor disagree", 
                                 "Agree","Strongly agree"),
    Q10_only_regulate_high_risk = fct_relevel(Q10_only_regulate_high_risk, 
                                 "Strongly disagree", "Disagree", 
                                 "Neither agree, nor disagree", 
                                 "Agree","Strongly agree"),
    Q10_developers_are_responsible = fct_relevel(Q10_developers_are_responsible,
                                 "Strongly disagree", "Disagree",
                                 "Neither agree, nor disagree",
                                 "Agree","Strongly agree"),
    Q9_engaging = fct_relevel(Q9_engaging,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    Q9_improving_user_experience = fct_relevel(Q9_improving_user_experience,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    Q9_missing_important_news = fct_relevel(Q9_missing_important_news,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    Q9_risking_privacy = fct_relevel(Q9_risking_privacy,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    Q9_spreading_misinfo = fct_relevel(Q9_spreading_misinfo,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    Q9_providing_relevant_news = fct_relevel(Q9_providing_relevant_news,
                              "Strongly disagree", "Disagree",
                              "Neither agree, nor disagree",
                              "Agree", "Strongly agree"),
    )

data = data %>%
  mutate(
    age_cat = fct_relevel(
      recode(nagecat,
        "18 t/m 24" = "18-24",
        "25 t/m 34" = "25-34",
        "35 t/m 44" = "35-44",
        "45 t/m 54" = "45-54",
        "55 t/m 70" = "55-70"
      ),
      "18-24", "25-34", "35-44", "45-54", "55-70"
    ),
    education = fct_relevel(education, "Low", "Middle", "High")
  )

# Trust preprocessing
data = data %>%
  mutate(trust_news = case_when(
    kari_trust_news_media < 4 ~ "low",
    kari_trust_news_media > 7 ~ "high",
    TRUE ~ 'medium'
  ),
  trust_news = fct_relevel(trust_news, 'low', 'medium', 'high'),
  trust_chatGPT = case_when(
    kari_trust_chatGPT < 4 ~ "low",
    kari_trust_chatGPT > 7 ~ "high",
    TRUE ~ 'medium'
  ),
  trust_chatGPT = fct_relevel(trust_chatGPT, 'low', 'medium', 'high')
  )

# Q5 feeling thermometers (0 = negative, 100 = positive): reshape the five
# items into long format so they can be compared as side-by-side box plots.
q5_long = data %>%
  select(
    country,
    `Check if the content is based on facts or reality`                                          = Q5_fact_check,
    `Identify the origins of the content, such as the author or the sources of information`      = Q5_identify_contents_origin,
    `Understand the writers' character, beliefs or personality`                                  = Q5_understanding_the_writer,
    `Understand which journalistic values, such as impartiality or accuracy, the content represents` = Q5_understanding_journalistic_values,
    `The ability to judge whether a human being was involved in the writing of the content`      = Q5_judging_human_involvement
  ) %>%
  pivot_longer(-country, names_to = "item", values_to = "value") %>%
  mutate(item = fct_inorder(item))

authenticity_rankings <- data %>%
  select(country, starts_with("Q4_")) %>%
  group_by(country) %>%
  summarise(across(starts_with("Q4_") & ends_with("numeric"), mean, na.rm = TRUE)) %>%
  rowwise() %>%
  mutate(across(starts_with("Q4_") & ends_with("numeric"),
                ~ rank(-c_across(starts_with("Q4_") & ends_with("numeric")))[which(c_across(starts_with("Q4_") & ends_with("numeric")) == .x)],
                .names = "{.col}_rank")) %>%
  ungroup() %>%
  dplyr::select(-ends_with("numeric"))

authenticity_bump = authenticity_rankings %>%
  pivot_longer(-country, names_to = "item", values_to = "rank") %>%
  mutate(
    item = recode(item,
                  "Q4_based_on_fact_numeric_rank"       = "Journalistic content that is based on facts or reality",
                  "Q4_identify_origin_numeric_rank"     = "Journalistic content where it is easy to identify the author and sources of information",
                  "Q4_expresses_character_numeric_rank" = "Journalistic content that expresses the writer's character, beliefs or personality",
                  "Q4_journ_values_numeric_rank"        = "Journalistic content that follows established journalistic values, such as honesty, impartiality and/or accuracy",
                  "Q4_written_by_a_human_numeric_rank"  = "Journalistic content that is written by a human being"
    ),
    rank = rank  # rank 1 = least important
  )
```

## Homepage

```{r}
home = create_page("Home", is_landing_page = TRUE) %>%
  add_text(
    "# Welcome to our Global AI journalism Monitor!", 
    "We surveyed xxxx people across six countries geographically and culturally diverse in April 2025 to get insights how people across the globe view journalistic AI.",
    "Specifically, we were interested in (1) how respondents understand authenticity in times of AI, (2) How journalistic AI use affects their perceptions and engagement with content, as well what journalistic principles should guide its use, and (3) how they want to see AI regulated.",
    "Feel free to explore our data and zoom in on key differences and similarities across countries.")

```

## Background variables

### GenAI use

```{r}
scale_1_10 = as.character(1:10)

GenAIuse = create_content(data = data, type = "bar") %>%
    add_viz(x_var = "GenAI_use", bar_type = "percent",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Overall", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "Netherlands",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Netherlands", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "Denmark",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Denmark", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "USA",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "USA", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "Brazil",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Brazil", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "South Africa",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "South Africa", tabgroup = "GenAI use") %>%
  add_viz(x_var = "GenAI_use", bar_type = "percent",
          filter = ~ country == "Japan",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Japan", tabgroup = "GenAI use")
 
GenAIuse %>% preview
```

### News Trust

```{r}
NewsTrust = create_content(data = data, type = "bar") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Overall", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "Netherlands",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Netherlands", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "Denmark",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Denmark", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "USA",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "USA", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "Brazil",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Brazil", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "South Africa",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "South Africa", tabgroup = "Trust/Trust in news media") %>%
  add_viz(x_var = "trust_news", bar_type = "percent", 
          filter = ~ country == "Japan",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Japan", tabgroup = "Trust/Trust in news media")

NewsTrust %>% preview
```

### ChatGPT Trust

```{r}
ChatGPTTrust = create_content(data = data, type = "bar") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Overall", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "Netherlands",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Netherlands", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "Denmark",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Denmark", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "USA",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "USA", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "Brazil",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Brazil", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "South Africa",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "South Africa", tabgroup = "Trust/Trust in ChatGPT") %>%
  add_viz(x_var = "trust_chatGPT", bar_type = "percent", 
          filter = ~ country == "Japan",
          x_label = "", y_label = "Percent (%)", tooltip_suffix = "%",
          title = "", title_tabset = "Japan", tabgroup = "Trust/Trust in ChatGPT")

ChatGPTTrust %>% preview
```

## Authenticity

### Authenticity Feelings

```{r}
therm_label = "Feeling thermometer (0 = negative, 100 = positive)"

authenticity_feelings = create_content(data = q5_long, type = "boxplot") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          title = "", title_tabset = "Overall",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "Netherlands",
          title = "", title_tabset = "Netherlands",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "Denmark",
          title = "", title_tabset = "Denmark",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "USA",
          title = "", title_tabset = "USA",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "Brazil",
          title = "", title_tabset = "Brazil",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "South Africa",
          title = "", title_tabset = "South Africa",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings") %>%
  add_viz(y_var = "value", x_var = "item", horizontal = TRUE,
          filter = ~ country == "Japan",
          title = "", title_tabset = "Japan",
          x_label = "", y_label = therm_label,
          tooltip_suffix = " / 100",
          tabgroup = "Authenticity feelings")

authenticity_feelings %>% preview()
```

### Authenticity Rankings

```{r}
countries_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan")

bump_viz = viz_timeline(
  data       = authenticity_bump,
  time_var   = "country",
  y_var      = "rank",
  group_var  = "item",
  agg        = "none",
  chart_type = "line",
  title      = "",
  y_label    = "Rank",
  y_min      = 1,
  y_max      = 5,
) %>%
  hc_yAxis(reversed = TRUE, min = 1, max = 5)

authenticity_ranking_viz = create_content(data = authenticity_bump, 
                                          type = "timeline") %>%   add_hc(bump_viz)

authenticity_ranking_viz %>% preview
```

## AI Journalism attitudes

### AI news engagement intentions

```{r}
q6_vars <- c("Q6_read", "Q6_share", "Q6_trust", 
             "Q6_talk", "Q6_ignore")

q6_labels = c(Q6_read = "Read", Q6_share = "Share", Q6_trust = "Trust",
              Q6_talk = "Talk About", Q6_ignore = "Ignore")

q6_order   = c("Very willing", "Somewhat willing", "Neutral",
               "Somewhat unwilling", "Very unwilling")
q6_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027")

AINewsEngagement = create_content(data = data, type = "stackedbar") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Overall", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="Netherlands",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Netherlands", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="Denmark",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Denmark", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="USA",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "USA", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="Brazil",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Brazil", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="South Africa",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "South Africa", tabgroup = "AI Journalism Attitudes/Willingness to Engage") %>%
  add_viz(x_vars = q6_vars,
          x_var_labels = q6_labels,
          stack_order = q6_order,
          color_palette = q6_palette,
          filter = ~ country =="Japan",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Japan", tabgroup = "AI Journalism Attitudes/Willingness to Engage")

AINewsEngagement %>% preview
```

### Attitudes towards hyperpersonalisation

```{r}
q9_vars <- c("Q9_engaging", "Q9_providing_relevant_news",
             "Q9_improving_user_experience",
             "Q9_risking_privacy",
             "Q9_missing_important_news",
             "Q9_spreading_misinfo")

q9_labels = c(Q9_engaging                  = "… helps me engage with news content",
              Q9_providing_relevant_news    = "… gives me more relevant news",
              Q9_improving_user_experience  = "… improves my user experience",
              Q9_risking_privacy            = "… risks my data privacy",
              Q9_missing_important_news     = "… makes me miss out on important news",
              Q9_spreading_misinfo          = "… leads to the spread of false and misleading information")

q9_order   = c("Strongly agree", "Agree", "Neither agree, nor disagree",
               "Disagree", "Strongly disagree")
q9_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027")

Hyperpersonalisation = create_content(data = data, type = "stackedbar") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Overall", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "Netherlands",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Netherlands", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "Denmark",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Denmark", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "USA",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "USA", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "Brazil",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Brazil", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "South Africa",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "South Africa", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation") %>%
  add_viz(x_vars = q9_vars,
          x_var_labels = q9_labels,
          stack_order = q9_order,
          color_palette = q9_palette,
          filter = ~ country == "Japan",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Japan", tabgroup = "AI Journalism Attitudes/Attitudes towards Hyperpersonalisation")

Hyperpersonalisation %>% preview
```

### Aspects influencing Credibility Judgements

```{r}
q8_vars <- c("Q8_trust_publisher", "Q8_realism",
             "Q8_misinfo_risk", "Q8_human_in_the_loop")

q8_labels = c(Q8_trust_publisher   = "How much you trust the publisher / news brand",
              Q8_realism           = "How realistic the content seems",
              Q8_misinfo_risk      = "The ability of AI to mislead",
              Q8_human_in_the_loop = "Whether it is clear in the article that a journalist checked the content before publishing")

q8_order   = c("Absolutely essential", "Very important",
               "Of average importance", "Of little importance", "Not important at all")
q8_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff")

Credibility = create_content(data = data, type = "stackedbar") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Overall", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "Netherlands",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Netherlands", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "Denmark",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Denmark", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "USA",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "USA", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "Brazil",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Brazil", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "South Africa",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "South Africa", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements") %>%
  add_viz(x_vars = q8_vars,
          x_var_labels = q8_labels,
          stack_order = q8_order,
          color_palette = q8_palette,
          filter = ~ country == "Japan",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Japan", tabgroup = "AI Journalism Attitudes/Aspects influencing Credibility Judgements")

Credibility %>% preview
```

### Journalistic principles

```{r}
#test
```

## Regulatory Preferences

### Regulatory models

```{r}
q10_vars <- c("Q10_developers_are_responsible", "Q10_free_companies",
             "Q10_government_decides", "Q10_involve_civil_society",
             "Q10_only_regulate_high_risk", "Q10_right_to_complain")

q10_labels = c(
  Q10_developers_are_responsible = "The developers of AI should make sure that the technology is safe to use and respects the rights of users.",
  Q10_free_companies             = "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.",
  Q10_government_decides         = "The government should determine when AI is safe to use.",
  Q10_involve_civil_society      = "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.",
  Q10_only_regulate_high_risk    = "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.",
  Q10_right_to_complain          = "Users should have a right to complain when their rights and interests are not respected."
)

q10_order   = c("Strongly agree", "Agree", "Neither agree, nor disagree",
                "Disagree", "Strongly disagree")
q10_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027")

RegulatoryModels = create_content(data = data, type = "stackedbar") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Overall", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "Netherlands",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Netherlands", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "Denmark",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Denmark", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "USA",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "USA", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "Brazil",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Brazil", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "South Africa",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "South Africa", tabgroup = "Regulatory Preferences/Attitudes towards Regulation") %>%
  add_viz(x_vars = q10_vars,
          x_var_labels = q10_labels,
          stack_order = q10_order,
          color_palette = q10_palette,
          filter = ~ country == "Japan",
          stacked_type = "percent",
          x_label = "", y_label = "Percent (%)",
          tooltip_suffix = "%", title = "",
          title_tabset = "Japan", tabgroup = "Regulatory Preferences/Attitudes towards Regulation")

RegulatoryModels %>% preview
```

### Regulatory Priorities

```{r}
q11_colors = c(
  "Economic wellbeing"                   = "#4E79A7",
  "Technological innovation"             = "#F28E2B",
  "Religious beliefs / local traditions" = "#E15759",
  "Human rights"                         = "#76B7B2",
  "Relationships with others"            = "#EDC948",
  "Environment"                          = "#59A14F",
  "State & national security"            = "#B07AA1"
)

item_order = function(df) {
  df %>%
    group_by(item) %>%
    summarise(pct = mean(mentioned), .groups = "drop") %>%
    arrange(desc(pct)) %>%
    pull(item)
}

q11_long = data %>%
  select(country, starts_with("Q11_")) %>%
  pivot_longer(-country, names_to = "item", values_to = "mentioned") %>%
  mutate(
    item = recode(item,
      "Q11_economic_wellbeing"                          = "Economic wellbeing",
      "Q11_technological_innovation"                    = "Technological innovation",
      "Q11_religious_beliefs_or_local_traditions"       = "Religious beliefs / local traditions",
      "Q11_human_rights"                                = "Human rights",
      "Q11_relationships_with_others"                   = "Relationships with others",
      "Q11_environment"                                 = "Environment",
      "Q11_interest_of_the_state_and_national_security" = "State & national security"
    ),
    mentioned = mentioned * 100
  )

Q11_mentions = create_content(data = q11_long, type = "bar") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long),
          color_palette = q11_colors[item_order(q11_long)],
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "Overall",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "Netherlands")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "Netherlands"))],
          filter = ~ country == "Netherlands",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities ", title_tabset = "Netherlands",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "Denmark")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "Denmark"))],          filter = ~ country == "Denmark",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "Denmark",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "USA")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "USA"))],
          filter = ~ country == "USA",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "USA",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "Brazil")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "Brazil"))],
          filter = ~ country == "Brazil",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "Brazil",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "South Africa")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "South Africa"))],
          filter = ~ country == "South Africa",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "South Africa",
          tabgroup = "Regulatory Preferences/Regulatory Priorities") %>%
  add_viz(x_var = "item", value_var = "mentioned", bar_type = "mean",
          x_order = item_order(q11_long %>% filter(country == "Japan")),
          color_palette = q11_colors[item_order(q11_long %>% filter(country == "Japan"))],
          filter = ~ country == "Japan",
          x_label = "", y_label = "% mentioned", tooltip_suffix = "%",
          title = "Regulatory Priorities", title_tabset = "Japan",
          tabgroup = "Regulatory Preferences/Regulatory Priorities")

Q11_mentions %>% preview
```

## Dashboard

```{r}
page_genai = create_page("GenAI use", data) %>%
  add_text('To measure this, we asked respondents: "In a typical week, how often do you use generative Artificial Intelligence (AI) applications like ChatGPT, Claude or DeepSeek?"') %>%
  add_content(GenAIuse)

page_trust = create_page("Trust", data) %>%
  add_text('To measure this, we asked respondents: "On a scale from 0 to 10, where 0 means "no trust at all" and 10 means "complete trust", how much do you trust [the news media in your country? / ChatGPT]"') %>%
  add_content(NewsTrust) %>%
  add_content(ChatGPTTrust)

#page_chatgpt_trust = create_page("Trust in ChatGPT", data) %>%
#  add_text("We measured this by asking ...") %>%
#  add_content(ChatGPTTrust)

page_authenticity_feelings = create_page("Authenticity Feelings", q5_long) %>%
  add_text('To measure this, we asked respondents: "How do you believe the use of AI to help create journalistic content, will affect your ability to do the following?"') %>%
  add_content(authenticity_feelings)

page_authenticity_rankings = create_page("Authenticity Rankings") %>%
  add_text('To measure this, we asked respondents: "What do you consider authentic journalistic content?  Please rank the following from 1 to 5, where 1 is most authentic and 5 is least authentic."') %>%
  add_content(authenticity_ranking_viz)

page_ai_journalism_attitudes = create_page("AI Journalism Attitudes", data) %>%
  add_text('To measure **Willingness to Engage**, we asked respondents: *"If you know from the beginning that journalistic content is generated with the help of AI, how willing are you to ..."*\n\n\n\nTo measure **Attitudes towards Hyperpersonalisation**, we asked respondents: *"Hyper-personalization uses generative AI to tailor news to your preferences and present it in flexible formatsways. For example, generative AI can change turn a news article into an audio clip or a summary, making it more engaging and relevant for you. To what extent do you agree with the following statements?"*\n\n\n\nTo measure **Aspects influencing Credibility Judgements**, we asked respondents: *"When you read an article that may be written by generative AI, how does each of the following factors influence how much you believe the content? "*') %>%
  add_content(AINewsEngagement) %>%
  add_content(Hyperpersonalisation) %>% 
  add_content(Credibility)

page_regulatory = create_page("Regulatory Preferences") %>%
  add_text('To measure **Regulatory Priorities**, we asked respondents: *"Which aspects of your life should AI regulation protect? Choose your top three aspects."*\n\n\n\nTo measure **Attitudes towards Regulation**, we asked respondents: *"To what extent do you agree with the following statements regarding AI regulation."*') %>%
  add_content(Q11_mentions) %>%
  add_content(RegulatoryModels)
```

```{r}
background_menu = navbar_menu(
  text = "Background variables",
  pages = c("GenAI use", "Trust")
)

authenticity_menu = navbar_menu(
  text = "Authenticity Perceptions",
  pages = c("Authenticity Feelings", "Authenticity Rankings")
)


AIJournalismDashboard = create_dashboard(
  title = "AI & Journalism Explorer",
  theme = "flatly",
  navbar_sections = list(background_menu, authenticity_menu),
  page_navigation = TRUE,
  pagination_position = "bottom"
) %>%
  add_pages(home, 
            page_genai, page_trust,
            page_authenticity_feelings, page_authenticity_rankings,
            page_ai_journalism_attitudes,
            page_regulatory)
```

## Inspect

```{r}
generate_dashboard(AIJournalismDashboard, render = TRUE)
```

## Publish

```{r}
generate_dashboard(AIJournalismDashboard, render = TRUE)

#publish_dashboard(
#  message = "First version",  
#  path = "/docs"               
#)

#To update your dashboard later, use:
#   update_dashboard(message = "Your update message")
```

```{r}
# Q5 broken down by country, one tab per question: each tab shows a box plot
# comparing the six countries on that single item's 0-100 thermometer.

country_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan")

Q5_by_question = create_content(data = q5_long, type = "boxplot") %>%
  add_viz(y_var = "value", x_var = "country", horizontal = TRUE,
          filter = ~ item == "Fact-checking",
          title = "Fact-checking", title_tabset = "Fact-checking",
          x_label = "", y_label = therm_label,
          x_order = country_order, tooltip_suffix = " / 100",
          tabgroup = "Q5 by question") %>%
  add_viz(y_var = "value", x_var = "country", horizontal = TRUE,
          filter = ~ item == "Identifying content origin",
          title = "Identifying content origin", title_tabset = "Identifying content origin",
          x_label = "", y_label = therm_label,
          x_order = country_order, tooltip_suffix = " / 100",
          tabgroup = "Q5 by question") %>%
  add_viz(y_var = "value", x_var = "country", horizontal = TRUE,
          filter = ~ item == "Understanding the writer",
          title = "Understanding the writer", title_tabset = "Understanding the writer",
          x_label = "", y_label = therm_label,
          x_order = country_order, tooltip_suffix = " / 100",
          tabgroup = "Q5 by question") %>%
  add_viz(y_var = "value", x_var = "country", horizontal = TRUE,
          filter = ~ item == "Understanding journalistic values",
          title = "Understanding journalistic values", title_tabset = "Understanding journalistic values",
          x_label = "", y_label = therm_label,
          x_order = country_order, tooltip_suffix = " / 100",
          tabgroup = "Q5 by question") %>%
  add_viz(y_var = "value", x_var = "country", horizontal = TRUE,
          filter = ~ item == "Judging human involvement",
          title = "Judging human involvement", title_tabset = "Judging human involvement",
          x_label = "", y_label = therm_label,
          x_order = country_order, tooltip_suffix = " / 100",
          tabgroup = "Q5 by question")

Q5_by_question %>% preview()
```
