---
title: "Q5 Feelings"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_34805obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_a2a3680f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(item == "Fact-checking")
data_filtered_ccaf1913 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(item == "Identifying content origin")
data_filtered_13ea1077 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(item == "Understanding the writer")
data_filtered_a131cc49 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(item == "Understanding journalistic values")
data_filtered_7767acc9 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(item == "Judging human involvement")

```


## Q5 — Feelings towards AI capabilities

Respondents rated each item on a 0–100 feeling thermometer, where 0 = negative and 100 = positive feelings. Each box shows the median, interquartile range and outliers; use the tabs to compare countries.


### By question

The same data viewed the other way around: each tab is a single question, with the six countries compared side by side.

## Q5 by country


::: {.panel-tabset}

### Netherlands

```{r q5-by-country}
# Netherlands
result <- viz_boxplot(
  data = data_filtered_03566455,
  title = "Netherlands",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r q5-by-country-2}
# Denmark
result <- viz_boxplot(
  data = data_filtered_beb8a137,
  title = "Denmark",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r q5-by-country-3}
# USA
result <- viz_boxplot(
  data = data_filtered_a1803a37,
  title = "USA",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r q5-by-country-4}
# Brazil
result <- viz_boxplot(
  data = data_filtered_6dcfcc28,
  title = "Brazil",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r q5-by-country-5}
# South Africa
result <- viz_boxplot(
  data = data_filtered_4bc4c9f5,
  title = "South Africa",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r q5-by-country-6}
# Japan
result <- viz_boxplot(
  data = data_filtered_0c062950,
  title = "Japan",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Overall

```{r q5-by-country-7}
# All countries
result <- viz_boxplot(
  data = data,
  title = "All countries",
  y_var = "value",
  x_var = "item",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## Q5 by question


::: {.panel-tabset}

### Fact-checking

```{r q5-by-question}
# Fact-checking
result <- viz_boxplot(
  data = data_filtered_a2a3680f,
  title = "Fact-checking",
  y_var = "value",
  x_var = "country",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  x_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan"),
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Identifying content origin

```{r q5-by-question-2}
# Identifying content origin
result <- viz_boxplot(
  data = data_filtered_ccaf1913,
  title = "Identifying content origin",
  y_var = "value",
  x_var = "country",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  x_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan"),
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Understanding the writer

```{r q5-by-question-3}
# Understanding the writer
result <- viz_boxplot(
  data = data_filtered_13ea1077,
  title = "Understanding the writer",
  y_var = "value",
  x_var = "country",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  x_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan"),
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Understanding journalistic values

```{r q5-by-question-4}
# Understanding journalistic values
result <- viz_boxplot(
  data = data_filtered_a131cc49,
  title = "Understanding journalistic values",
  y_var = "value",
  x_var = "country",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  x_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan"),
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Judging human involvement

```{r q5-by-question-5}
# Judging human involvement
result <- viz_boxplot(
  data = data_filtered_7767acc9,
  title = "Judging human involvement",
  y_var = "value",
  x_var = "country",
  horizontal = TRUE,
  x_label = "",
  y_label = "Feeling thermometer (0 = negative, 100 = positive)",
  x_order = c("Netherlands", "Denmark", "USA", "Brazil", "South Africa", "Japan"),
  tooltip_suffix = " / 100"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

