---
title: "Aspects influencing Credibility Judgements"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_6961obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_7d7cd613 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(!is.na(country))
data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_3fb005e3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24")
data_filtered_6348e589 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Netherlands")
data_filtered_25853ff4 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Denmark")
data_filtered_a3d5a06f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "USA")
data_filtered_d32c292c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Brazil")
data_filtered_915c3792 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "South Africa")
data_filtered_d29ab143 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Japan")
data_filtered_92fc3831 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34")
data_filtered_557767d0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Netherlands")
data_filtered_b614abb1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Denmark")
data_filtered_f80bceec <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "USA")
data_filtered_9c9acee6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Brazil")
data_filtered_cc6389e1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "South Africa")
data_filtered_1e8794e2 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Japan")
data_filtered_330fa49b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44")
data_filtered_7b008396 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Netherlands")
data_filtered_3cbc27a7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Denmark")
data_filtered_dd424d3e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "USA")
data_filtered_a9d7350c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Brazil")
data_filtered_10069476 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "South Africa")
data_filtered_5032d21e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Japan")
data_filtered_3933346b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54")
data_filtered_d8ff95a9 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Netherlands")
data_filtered_36d54459 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Denmark")
data_filtered_48aa5753 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "USA")
data_filtered_7b086cf6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Brazil")
data_filtered_5a76236d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "South Africa")
data_filtered_46d84a62 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Japan")
data_filtered_3a83579f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70")
data_filtered_442de25e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Netherlands")
data_filtered_090a4f1e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Denmark")
data_filtered_8452c6af <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "USA")
data_filtered_9479d505 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Brazil")
data_filtered_c7ec7e9a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "South Africa")
data_filtered_f6fc64ce <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Japan")
data_filtered_cc59ed7a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female")
data_filtered_a025f9db <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Netherlands")
data_filtered_728c9564 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Denmark")
data_filtered_720e3a90 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "USA")
data_filtered_8854d5bd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Brazil")
data_filtered_ea67835c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "South Africa")
data_filtered_accea8ca <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Japan")
data_filtered_8ef3cd03 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male")
data_filtered_dd845ffc <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Netherlands")
data_filtered_a3c2602c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Denmark")
data_filtered_8606dde3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "USA")
data_filtered_3bf0d168 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Brazil")
data_filtered_7ddd92b7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "South Africa")
data_filtered_3ce049e8 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Japan")
data_filtered_656f8f39 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low")
data_filtered_e18edb59 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Netherlands")
data_filtered_2b9b5e86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Denmark")
data_filtered_61039118 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "USA")
data_filtered_488119b3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Brazil")
data_filtered_593bd084 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "South Africa")
data_filtered_577c6c25 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Japan")
data_filtered_51ea7279 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle")
data_filtered_cae4b485 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Netherlands")
data_filtered_ecf84d0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Denmark")
data_filtered_1c870641 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "USA")
data_filtered_57056314 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Brazil")
data_filtered_eb413204 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "South Africa")
data_filtered_621f4df0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Japan")
data_filtered_42f6fc86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High")
data_filtered_a5527f6f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Netherlands")
data_filtered_cf3b699b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Denmark")
data_filtered_b2522cfd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "USA")
data_filtered_339bde9d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Brazil")
data_filtered_46a4019a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "South Africa")
data_filtered_82c5bf0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Japan")

```


To measure the importance of specific aspects which influence the credibility of AI-supported journalistic content, we asked the following: *When you read an article that may be written by generative AI, how does each of the following factors influence how much you believe the content?*


<div style='height: 2rem;'></div>

## Aspects influencing Credibility Judgements across countries


::: {.panel-tabset}

### All Countries

```{r aspects-influencing-credibility-judgements-across}
# 
result <- viz_stackedbar(
  data = data_filtered_7d7cd613,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Netherlands

```{r aspects-influencing-credibility-judgements-across-2}
# 
result <- viz_stackedbar(
  data = data_filtered_03566455,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r aspects-influencing-credibility-judgements-across-3}
# 
result <- viz_stackedbar(
  data = data_filtered_beb8a137,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r aspects-influencing-credibility-judgements-across-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a1803a37,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r aspects-influencing-credibility-judgements-across-5}
# 
result <- viz_stackedbar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r aspects-influencing-credibility-judgements-across-6}
# 
result <- viz_stackedbar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r aspects-influencing-credibility-judgements-across-7}
# 
result <- viz_stackedbar(
  data = data_filtered_0c062950,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## Aspects influencing Credibility Judgements among Different Subgroups


::: {.panel-tabset}

### By Age Group


::: {.panel-tabset}

##### 18-24


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d}
# 
result <- viz_stackedbar(
  data = data_filtered_3fb005e3,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-2}
# 
result <- viz_stackedbar(
  data = data_filtered_6348e589,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-3}
# 
result <- viz_stackedbar(
  data = data_filtered_25853ff4,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a3d5a06f,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-5}
# 
result <- viz_stackedbar(
  data = data_filtered_d32c292c,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-6}
# 
result <- viz_stackedbar(
  data = data_filtered_915c3792,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-7}
# 
result <- viz_stackedbar(
  data = data_filtered_d29ab143,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 25-34


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-8}
# 
result <- viz_stackedbar(
  data = data_filtered_92fc3831,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-9}
# 
result <- viz_stackedbar(
  data = data_filtered_557767d0,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-10}
# 
result <- viz_stackedbar(
  data = data_filtered_b614abb1,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-11}
# 
result <- viz_stackedbar(
  data = data_filtered_f80bceec,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-12}
# 
result <- viz_stackedbar(
  data = data_filtered_9c9acee6,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-13}
# 
result <- viz_stackedbar(
  data = data_filtered_cc6389e1,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-14}
# 
result <- viz_stackedbar(
  data = data_filtered_1e8794e2,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 35-44


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-15}
# 
result <- viz_stackedbar(
  data = data_filtered_330fa49b,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-16}
# 
result <- viz_stackedbar(
  data = data_filtered_7b008396,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-17}
# 
result <- viz_stackedbar(
  data = data_filtered_3cbc27a7,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-18}
# 
result <- viz_stackedbar(
  data = data_filtered_dd424d3e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-19}
# 
result <- viz_stackedbar(
  data = data_filtered_a9d7350c,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-20}
# 
result <- viz_stackedbar(
  data = data_filtered_10069476,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-21}
# 
result <- viz_stackedbar(
  data = data_filtered_5032d21e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 45-54


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-22}
# 
result <- viz_stackedbar(
  data = data_filtered_3933346b,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-23}
# 
result <- viz_stackedbar(
  data = data_filtered_d8ff95a9,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-24}
# 
result <- viz_stackedbar(
  data = data_filtered_36d54459,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-25}
# 
result <- viz_stackedbar(
  data = data_filtered_48aa5753,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-26}
# 
result <- viz_stackedbar(
  data = data_filtered_7b086cf6,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-27}
# 
result <- viz_stackedbar(
  data = data_filtered_5a76236d,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-28}
# 
result <- viz_stackedbar(
  data = data_filtered_46d84a62,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 55-70


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-29}
# 
result <- viz_stackedbar(
  data = data_filtered_3a83579f,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-30}
# 
result <- viz_stackedbar(
  data = data_filtered_442de25e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-31}
# 
result <- viz_stackedbar(
  data = data_filtered_090a4f1e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-32}
# 
result <- viz_stackedbar(
  data = data_filtered_8452c6af,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-33}
# 
result <- viz_stackedbar(
  data = data_filtered_9479d505,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-34}
# 
result <- viz_stackedbar(
  data = data_filtered_c7ec7e9a,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-35}
# 
result <- viz_stackedbar(
  data = data_filtered_f6fc64ce,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Gender


::: {.panel-tabset}

##### Female


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-36}
# 
result <- viz_stackedbar(
  data = data_filtered_cc59ed7a,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-37}
# 
result <- viz_stackedbar(
  data = data_filtered_a025f9db,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-38}
# 
result <- viz_stackedbar(
  data = data_filtered_728c9564,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-39}
# 
result <- viz_stackedbar(
  data = data_filtered_720e3a90,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-40}
# 
result <- viz_stackedbar(
  data = data_filtered_8854d5bd,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-41}
# 
result <- viz_stackedbar(
  data = data_filtered_ea67835c,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-42}
# 
result <- viz_stackedbar(
  data = data_filtered_accea8ca,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Male


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-43}
# 
result <- viz_stackedbar(
  data = data_filtered_8ef3cd03,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-44}
# 
result <- viz_stackedbar(
  data = data_filtered_dd845ffc,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-45}
# 
result <- viz_stackedbar(
  data = data_filtered_a3c2602c,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-46}
# 
result <- viz_stackedbar(
  data = data_filtered_8606dde3,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-47}
# 
result <- viz_stackedbar(
  data = data_filtered_3bf0d168,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-48}
# 
result <- viz_stackedbar(
  data = data_filtered_7ddd92b7,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-49}
# 
result <- viz_stackedbar(
  data = data_filtered_3ce049e8,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Education


::: {.panel-tabset}

##### Low


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-50}
# 
result <- viz_stackedbar(
  data = data_filtered_656f8f39,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-51}
# 
result <- viz_stackedbar(
  data = data_filtered_e18edb59,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-52}
# 
result <- viz_stackedbar(
  data = data_filtered_2b9b5e86,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-53}
# 
result <- viz_stackedbar(
  data = data_filtered_61039118,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-54}
# 
result <- viz_stackedbar(
  data = data_filtered_488119b3,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-55}
# 
result <- viz_stackedbar(
  data = data_filtered_593bd084,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-56}
# 
result <- viz_stackedbar(
  data = data_filtered_577c6c25,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Middle


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-57}
# 
result <- viz_stackedbar(
  data = data_filtered_51ea7279,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-58}
# 
result <- viz_stackedbar(
  data = data_filtered_cae4b485,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-59}
# 
result <- viz_stackedbar(
  data = data_filtered_ecf84d0e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-60}
# 
result <- viz_stackedbar(
  data = data_filtered_1c870641,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-61}
# 
result <- viz_stackedbar(
  data = data_filtered_57056314,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-62}
# 
result <- viz_stackedbar(
  data = data_filtered_eb413204,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-63}
# 
result <- viz_stackedbar(
  data = data_filtered_621f4df0,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### High


::: {.panel-tabset}

###### All Countries

```{r aspects-influencing-credibility-judgements-among-d-64}
# 
result <- viz_stackedbar(
  data = data_filtered_42f6fc86,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r aspects-influencing-credibility-judgements-among-d-65}
# 
result <- viz_stackedbar(
  data = data_filtered_a5527f6f,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r aspects-influencing-credibility-judgements-among-d-66}
# 
result <- viz_stackedbar(
  data = data_filtered_cf3b699b,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r aspects-influencing-credibility-judgements-among-d-67}
# 
result <- viz_stackedbar(
  data = data_filtered_b2522cfd,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r aspects-influencing-credibility-judgements-among-d-68}
# 
result <- viz_stackedbar(
  data = data_filtered_339bde9d,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r aspects-influencing-credibility-judgements-among-d-69}
# 
result <- viz_stackedbar(
  data = data_filtered_46a4019a,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r aspects-influencing-credibility-judgements-among-d-70}
# 
result <- viz_stackedbar(
  data = data_filtered_82c5bf0e,
  title = "",
  x_vars = c("Q8_trust_publisher", "Q8_realism", "Q8_misinfo_risk", "Q8_human_in_the_loop"),
  x_var_labels = c("How much you trust the publisher / news brand", "How realistic the content seems", "The ability of AI to mislead", "Whether it is clear in the article that a journalist checked the content before publishing"),
  stack_order = c("Absolutely essential", "Very important", "Of average importance", "Of little importance", "Not important at all"),
  color_palette = c("#08306b", "#2171b5", "#6baed6", "#c6dbef", "#f7fbff"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


:::

