---
title: "Attitudes towards Hyperpersonalisation"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_6961obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_7d7cd613 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(!is.na(country))
data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_3fb005e3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24")
data_filtered_6348e589 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Netherlands")
data_filtered_25853ff4 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Denmark")
data_filtered_a3d5a06f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "USA")
data_filtered_d32c292c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Brazil")
data_filtered_915c3792 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "South Africa")
data_filtered_d29ab143 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Japan")
data_filtered_92fc3831 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34")
data_filtered_557767d0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Netherlands")
data_filtered_b614abb1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Denmark")
data_filtered_f80bceec <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "USA")
data_filtered_9c9acee6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Brazil")
data_filtered_cc6389e1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "South Africa")
data_filtered_1e8794e2 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Japan")
data_filtered_330fa49b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44")
data_filtered_7b008396 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Netherlands")
data_filtered_3cbc27a7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Denmark")
data_filtered_dd424d3e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "USA")
data_filtered_a9d7350c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Brazil")
data_filtered_10069476 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "South Africa")
data_filtered_5032d21e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Japan")
data_filtered_3933346b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54")
data_filtered_d8ff95a9 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Netherlands")
data_filtered_36d54459 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Denmark")
data_filtered_48aa5753 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "USA")
data_filtered_7b086cf6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Brazil")
data_filtered_5a76236d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "South Africa")
data_filtered_46d84a62 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Japan")
data_filtered_3a83579f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70")
data_filtered_442de25e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Netherlands")
data_filtered_090a4f1e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Denmark")
data_filtered_8452c6af <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "USA")
data_filtered_9479d505 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Brazil")
data_filtered_c7ec7e9a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "South Africa")
data_filtered_f6fc64ce <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Japan")
data_filtered_cc59ed7a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female")
data_filtered_a025f9db <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Netherlands")
data_filtered_728c9564 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Denmark")
data_filtered_720e3a90 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "USA")
data_filtered_8854d5bd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Brazil")
data_filtered_ea67835c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "South Africa")
data_filtered_accea8ca <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Japan")
data_filtered_8ef3cd03 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male")
data_filtered_dd845ffc <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Netherlands")
data_filtered_a3c2602c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Denmark")
data_filtered_8606dde3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "USA")
data_filtered_3bf0d168 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Brazil")
data_filtered_7ddd92b7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "South Africa")
data_filtered_3ce049e8 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Japan")
data_filtered_656f8f39 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low")
data_filtered_e18edb59 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Netherlands")
data_filtered_2b9b5e86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Denmark")
data_filtered_61039118 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "USA")
data_filtered_488119b3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Brazil")
data_filtered_593bd084 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "South Africa")
data_filtered_577c6c25 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Japan")
data_filtered_51ea7279 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle")
data_filtered_cae4b485 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Netherlands")
data_filtered_ecf84d0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Denmark")
data_filtered_1c870641 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "USA")
data_filtered_57056314 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Brazil")
data_filtered_eb413204 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "South Africa")
data_filtered_621f4df0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Japan")
data_filtered_42f6fc86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High")
data_filtered_a5527f6f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Netherlands")
data_filtered_cf3b699b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Denmark")
data_filtered_b2522cfd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "USA")
data_filtered_339bde9d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Brazil")
data_filtered_46a4019a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "South Africa")
data_filtered_82c5bf0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Japan")

```


***Definition:*** Hyperpersonalization uses generative AI to tailor news to individuals’ preferences and present it in flexible formats and ways. For example, generative AI can turn a news article into an audio clip or a short summary, making it more engaging and relevant for different individuals.

To measure what people think about hyperpeersonalisation, we asked our respondents to what extent they agree with the statements below:


<div style='height: 2rem;'></div>

## Attitudes towards Hyperpersonalisation across countries


::: {.panel-tabset}

### All Countries

```{r attitudes-towards-hyperpersonalisation-across-coun}
# 
result <- viz_stackedbar(
  data = data_filtered_7d7cd613,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Netherlands

```{r attitudes-towards-hyperpersonalisation-across-coun-2}
# 
result <- viz_stackedbar(
  data = data_filtered_03566455,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r attitudes-towards-hyperpersonalisation-across-coun-3}
# 
result <- viz_stackedbar(
  data = data_filtered_beb8a137,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r attitudes-towards-hyperpersonalisation-across-coun-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a1803a37,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r attitudes-towards-hyperpersonalisation-across-coun-5}
# 
result <- viz_stackedbar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r attitudes-towards-hyperpersonalisation-across-coun-6}
# 
result <- viz_stackedbar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r attitudes-towards-hyperpersonalisation-across-coun-7}
# 
result <- viz_stackedbar(
  data = data_filtered_0c062950,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## Attitudes towards Hyperpersonalisation among Different Subgroups


::: {.panel-tabset}

### By Age Group


::: {.panel-tabset}

##### 18-24


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe}
# 
result <- viz_stackedbar(
  data = data_filtered_3fb005e3,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-2}
# 
result <- viz_stackedbar(
  data = data_filtered_6348e589,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-3}
# 
result <- viz_stackedbar(
  data = data_filtered_25853ff4,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a3d5a06f,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-5}
# 
result <- viz_stackedbar(
  data = data_filtered_d32c292c,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-6}
# 
result <- viz_stackedbar(
  data = data_filtered_915c3792,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-7}
# 
result <- viz_stackedbar(
  data = data_filtered_d29ab143,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 25-34


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-8}
# 
result <- viz_stackedbar(
  data = data_filtered_92fc3831,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-9}
# 
result <- viz_stackedbar(
  data = data_filtered_557767d0,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-10}
# 
result <- viz_stackedbar(
  data = data_filtered_b614abb1,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-11}
# 
result <- viz_stackedbar(
  data = data_filtered_f80bceec,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-12}
# 
result <- viz_stackedbar(
  data = data_filtered_9c9acee6,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-13}
# 
result <- viz_stackedbar(
  data = data_filtered_cc6389e1,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-14}
# 
result <- viz_stackedbar(
  data = data_filtered_1e8794e2,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 35-44


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-15}
# 
result <- viz_stackedbar(
  data = data_filtered_330fa49b,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-16}
# 
result <- viz_stackedbar(
  data = data_filtered_7b008396,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-17}
# 
result <- viz_stackedbar(
  data = data_filtered_3cbc27a7,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-18}
# 
result <- viz_stackedbar(
  data = data_filtered_dd424d3e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-19}
# 
result <- viz_stackedbar(
  data = data_filtered_a9d7350c,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-20}
# 
result <- viz_stackedbar(
  data = data_filtered_10069476,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-21}
# 
result <- viz_stackedbar(
  data = data_filtered_5032d21e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 45-54


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-22}
# 
result <- viz_stackedbar(
  data = data_filtered_3933346b,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-23}
# 
result <- viz_stackedbar(
  data = data_filtered_d8ff95a9,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-24}
# 
result <- viz_stackedbar(
  data = data_filtered_36d54459,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-25}
# 
result <- viz_stackedbar(
  data = data_filtered_48aa5753,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-26}
# 
result <- viz_stackedbar(
  data = data_filtered_7b086cf6,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-27}
# 
result <- viz_stackedbar(
  data = data_filtered_5a76236d,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-28}
# 
result <- viz_stackedbar(
  data = data_filtered_46d84a62,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 55-70


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-29}
# 
result <- viz_stackedbar(
  data = data_filtered_3a83579f,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-30}
# 
result <- viz_stackedbar(
  data = data_filtered_442de25e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-31}
# 
result <- viz_stackedbar(
  data = data_filtered_090a4f1e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-32}
# 
result <- viz_stackedbar(
  data = data_filtered_8452c6af,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-33}
# 
result <- viz_stackedbar(
  data = data_filtered_9479d505,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-34}
# 
result <- viz_stackedbar(
  data = data_filtered_c7ec7e9a,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-35}
# 
result <- viz_stackedbar(
  data = data_filtered_f6fc64ce,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Gender


::: {.panel-tabset}

##### Female


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-36}
# 
result <- viz_stackedbar(
  data = data_filtered_cc59ed7a,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-37}
# 
result <- viz_stackedbar(
  data = data_filtered_a025f9db,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-38}
# 
result <- viz_stackedbar(
  data = data_filtered_728c9564,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-39}
# 
result <- viz_stackedbar(
  data = data_filtered_720e3a90,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-40}
# 
result <- viz_stackedbar(
  data = data_filtered_8854d5bd,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-41}
# 
result <- viz_stackedbar(
  data = data_filtered_ea67835c,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-42}
# 
result <- viz_stackedbar(
  data = data_filtered_accea8ca,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Male


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-43}
# 
result <- viz_stackedbar(
  data = data_filtered_8ef3cd03,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-44}
# 
result <- viz_stackedbar(
  data = data_filtered_dd845ffc,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-45}
# 
result <- viz_stackedbar(
  data = data_filtered_a3c2602c,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-46}
# 
result <- viz_stackedbar(
  data = data_filtered_8606dde3,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-47}
# 
result <- viz_stackedbar(
  data = data_filtered_3bf0d168,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-48}
# 
result <- viz_stackedbar(
  data = data_filtered_7ddd92b7,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-49}
# 
result <- viz_stackedbar(
  data = data_filtered_3ce049e8,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Education


::: {.panel-tabset}

##### Low


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-50}
# 
result <- viz_stackedbar(
  data = data_filtered_656f8f39,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-51}
# 
result <- viz_stackedbar(
  data = data_filtered_e18edb59,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-52}
# 
result <- viz_stackedbar(
  data = data_filtered_2b9b5e86,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-53}
# 
result <- viz_stackedbar(
  data = data_filtered_61039118,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-54}
# 
result <- viz_stackedbar(
  data = data_filtered_488119b3,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-55}
# 
result <- viz_stackedbar(
  data = data_filtered_593bd084,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-56}
# 
result <- viz_stackedbar(
  data = data_filtered_577c6c25,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Middle


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-57}
# 
result <- viz_stackedbar(
  data = data_filtered_51ea7279,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-58}
# 
result <- viz_stackedbar(
  data = data_filtered_cae4b485,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-59}
# 
result <- viz_stackedbar(
  data = data_filtered_ecf84d0e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-60}
# 
result <- viz_stackedbar(
  data = data_filtered_1c870641,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-61}
# 
result <- viz_stackedbar(
  data = data_filtered_57056314,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-62}
# 
result <- viz_stackedbar(
  data = data_filtered_eb413204,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-63}
# 
result <- viz_stackedbar(
  data = data_filtered_621f4df0,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### High


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-hyperpersonalisation-among-diffe-64}
# 
result <- viz_stackedbar(
  data = data_filtered_42f6fc86,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-hyperpersonalisation-among-diffe-65}
# 
result <- viz_stackedbar(
  data = data_filtered_a5527f6f,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-hyperpersonalisation-among-diffe-66}
# 
result <- viz_stackedbar(
  data = data_filtered_cf3b699b,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-hyperpersonalisation-among-diffe-67}
# 
result <- viz_stackedbar(
  data = data_filtered_b2522cfd,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-hyperpersonalisation-among-diffe-68}
# 
result <- viz_stackedbar(
  data = data_filtered_339bde9d,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-hyperpersonalisation-among-diffe-69}
# 
result <- viz_stackedbar(
  data = data_filtered_46a4019a,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-hyperpersonalisation-among-diffe-70}
# 
result <- viz_stackedbar(
  data = data_filtered_82c5bf0e,
  title = "",
  x_vars = c("Q9_engaging", "Q9_providing_relevant_news", "Q9_improving_user_experience", "Q9_risking_privacy", "Q9_missing_important_news", "Q9_spreading_misinfo"),
  x_var_labels = c("Hyperpersonalisation helps me engage with news content", "Hyperpersonalisation gives me more relevant news", "Hyperpersonalisation improves my user experience", "Hyperpersonalisation risks my data privacy", "Hyperpersonalisation makes me miss out on important news", "Hyperpersonalisation leads to the spread of false and misleading information"),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


:::

