---
title: "Attitudes towards Regulation"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_6961obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_7d7cd613 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(!is.na(country))
data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_3fb005e3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24")
data_filtered_6348e589 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Netherlands")
data_filtered_25853ff4 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Denmark")
data_filtered_a3d5a06f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "USA")
data_filtered_d32c292c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Brazil")
data_filtered_915c3792 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "South Africa")
data_filtered_d29ab143 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "18-24" & country == "Japan")
data_filtered_92fc3831 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34")
data_filtered_557767d0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Netherlands")
data_filtered_b614abb1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Denmark")
data_filtered_f80bceec <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "USA")
data_filtered_9c9acee6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Brazil")
data_filtered_cc6389e1 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "South Africa")
data_filtered_1e8794e2 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "25-34" & country == "Japan")
data_filtered_330fa49b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44")
data_filtered_7b008396 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Netherlands")
data_filtered_3cbc27a7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Denmark")
data_filtered_dd424d3e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "USA")
data_filtered_a9d7350c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Brazil")
data_filtered_10069476 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "South Africa")
data_filtered_5032d21e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "35-44" & country == "Japan")
data_filtered_3933346b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54")
data_filtered_d8ff95a9 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Netherlands")
data_filtered_36d54459 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Denmark")
data_filtered_48aa5753 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "USA")
data_filtered_7b086cf6 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Brazil")
data_filtered_5a76236d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "South Africa")
data_filtered_46d84a62 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "45-54" & country == "Japan")
data_filtered_3a83579f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70")
data_filtered_442de25e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Netherlands")
data_filtered_090a4f1e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Denmark")
data_filtered_8452c6af <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "USA")
data_filtered_9479d505 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Brazil")
data_filtered_c7ec7e9a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "South Africa")
data_filtered_f6fc64ce <- dashboardr:::.convert_haven(data) %>% dplyr::filter(age_cat == "55-70" & country == "Japan")
data_filtered_cc59ed7a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female")
data_filtered_a025f9db <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Netherlands")
data_filtered_728c9564 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Denmark")
data_filtered_720e3a90 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "USA")
data_filtered_8854d5bd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Brazil")
data_filtered_ea67835c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "South Africa")
data_filtered_accea8ca <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Female" & country == "Japan")
data_filtered_8ef3cd03 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male")
data_filtered_dd845ffc <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Netherlands")
data_filtered_a3c2602c <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Denmark")
data_filtered_8606dde3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "USA")
data_filtered_3bf0d168 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Brazil")
data_filtered_7ddd92b7 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "South Africa")
data_filtered_3ce049e8 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender == "Male" & country == "Japan")
data_filtered_656f8f39 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low")
data_filtered_e18edb59 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Netherlands")
data_filtered_2b9b5e86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Denmark")
data_filtered_61039118 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "USA")
data_filtered_488119b3 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Brazil")
data_filtered_593bd084 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "South Africa")
data_filtered_577c6c25 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Low" & country == "Japan")
data_filtered_51ea7279 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle")
data_filtered_cae4b485 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Netherlands")
data_filtered_ecf84d0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Denmark")
data_filtered_1c870641 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "USA")
data_filtered_57056314 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Brazil")
data_filtered_eb413204 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "South Africa")
data_filtered_621f4df0 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "Middle" & country == "Japan")
data_filtered_42f6fc86 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High")
data_filtered_a5527f6f <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Netherlands")
data_filtered_cf3b699b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Denmark")
data_filtered_b2522cfd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "USA")
data_filtered_339bde9d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Brazil")
data_filtered_46a4019a <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "South Africa")
data_filtered_82c5bf0e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(education == "High" & country == "Japan")

```


To measure what people think AI regulation should do and who should be held accountable, we asked our respondents to indicate to what extent they agree with the following statements regarding AI regulation.


<div style='height: 2rem;'></div>

## Attitudes towards Regulation across countries


::: {.panel-tabset}

### All Countries

```{r attitudes-towards-regulation-across-countries}
# 
result <- viz_stackedbar(
  data = data_filtered_7d7cd613,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Netherlands

```{r attitudes-towards-regulation-across-countries-2}
# 
result <- viz_stackedbar(
  data = data_filtered_03566455,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r attitudes-towards-regulation-across-countries-3}
# 
result <- viz_stackedbar(
  data = data_filtered_beb8a137,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r attitudes-towards-regulation-across-countries-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a1803a37,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r attitudes-towards-regulation-across-countries-5}
# 
result <- viz_stackedbar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r attitudes-towards-regulation-across-countries-6}
# 
result <- viz_stackedbar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r attitudes-towards-regulation-across-countries-7}
# 
result <- viz_stackedbar(
  data = data_filtered_0c062950,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## Attitudes towards Regulation among Different Subgroups


::: {.panel-tabset}

### By Age Group


::: {.panel-tabset}

##### 18-24


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr}
# 
result <- viz_stackedbar(
  data = data_filtered_3fb005e3,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-2}
# 
result <- viz_stackedbar(
  data = data_filtered_6348e589,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-3}
# 
result <- viz_stackedbar(
  data = data_filtered_25853ff4,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-4}
# 
result <- viz_stackedbar(
  data = data_filtered_a3d5a06f,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-5}
# 
result <- viz_stackedbar(
  data = data_filtered_d32c292c,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-6}
# 
result <- viz_stackedbar(
  data = data_filtered_915c3792,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-7}
# 
result <- viz_stackedbar(
  data = data_filtered_d29ab143,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 25-34


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-8}
# 
result <- viz_stackedbar(
  data = data_filtered_92fc3831,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-9}
# 
result <- viz_stackedbar(
  data = data_filtered_557767d0,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-10}
# 
result <- viz_stackedbar(
  data = data_filtered_b614abb1,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-11}
# 
result <- viz_stackedbar(
  data = data_filtered_f80bceec,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-12}
# 
result <- viz_stackedbar(
  data = data_filtered_9c9acee6,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-13}
# 
result <- viz_stackedbar(
  data = data_filtered_cc6389e1,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-14}
# 
result <- viz_stackedbar(
  data = data_filtered_1e8794e2,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 35-44


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-15}
# 
result <- viz_stackedbar(
  data = data_filtered_330fa49b,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-16}
# 
result <- viz_stackedbar(
  data = data_filtered_7b008396,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-17}
# 
result <- viz_stackedbar(
  data = data_filtered_3cbc27a7,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-18}
# 
result <- viz_stackedbar(
  data = data_filtered_dd424d3e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-19}
# 
result <- viz_stackedbar(
  data = data_filtered_a9d7350c,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-20}
# 
result <- viz_stackedbar(
  data = data_filtered_10069476,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-21}
# 
result <- viz_stackedbar(
  data = data_filtered_5032d21e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 45-54


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-22}
# 
result <- viz_stackedbar(
  data = data_filtered_3933346b,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-23}
# 
result <- viz_stackedbar(
  data = data_filtered_d8ff95a9,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-24}
# 
result <- viz_stackedbar(
  data = data_filtered_36d54459,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-25}
# 
result <- viz_stackedbar(
  data = data_filtered_48aa5753,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-26}
# 
result <- viz_stackedbar(
  data = data_filtered_7b086cf6,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-27}
# 
result <- viz_stackedbar(
  data = data_filtered_5a76236d,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-28}
# 
result <- viz_stackedbar(
  data = data_filtered_46d84a62,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### 55-70


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-29}
# 
result <- viz_stackedbar(
  data = data_filtered_3a83579f,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-30}
# 
result <- viz_stackedbar(
  data = data_filtered_442de25e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-31}
# 
result <- viz_stackedbar(
  data = data_filtered_090a4f1e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-32}
# 
result <- viz_stackedbar(
  data = data_filtered_8452c6af,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-33}
# 
result <- viz_stackedbar(
  data = data_filtered_9479d505,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-34}
# 
result <- viz_stackedbar(
  data = data_filtered_c7ec7e9a,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-35}
# 
result <- viz_stackedbar(
  data = data_filtered_f6fc64ce,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Gender


::: {.panel-tabset}

##### Female


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-36}
# 
result <- viz_stackedbar(
  data = data_filtered_cc59ed7a,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-37}
# 
result <- viz_stackedbar(
  data = data_filtered_a025f9db,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-38}
# 
result <- viz_stackedbar(
  data = data_filtered_728c9564,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-39}
# 
result <- viz_stackedbar(
  data = data_filtered_720e3a90,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-40}
# 
result <- viz_stackedbar(
  data = data_filtered_8854d5bd,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-41}
# 
result <- viz_stackedbar(
  data = data_filtered_ea67835c,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-42}
# 
result <- viz_stackedbar(
  data = data_filtered_accea8ca,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Male


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-43}
# 
result <- viz_stackedbar(
  data = data_filtered_8ef3cd03,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-44}
# 
result <- viz_stackedbar(
  data = data_filtered_dd845ffc,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-45}
# 
result <- viz_stackedbar(
  data = data_filtered_a3c2602c,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-46}
# 
result <- viz_stackedbar(
  data = data_filtered_8606dde3,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-47}
# 
result <- viz_stackedbar(
  data = data_filtered_3bf0d168,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-48}
# 
result <- viz_stackedbar(
  data = data_filtered_7ddd92b7,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-49}
# 
result <- viz_stackedbar(
  data = data_filtered_3ce049e8,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = ""
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


### By Education


::: {.panel-tabset}

##### Low


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-50}
# 
result <- viz_stackedbar(
  data = data_filtered_656f8f39,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-51}
# 
result <- viz_stackedbar(
  data = data_filtered_e18edb59,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-52}
# 
result <- viz_stackedbar(
  data = data_filtered_2b9b5e86,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-53}
# 
result <- viz_stackedbar(
  data = data_filtered_61039118,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-54}
# 
result <- viz_stackedbar(
  data = data_filtered_488119b3,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-55}
# 
result <- viz_stackedbar(
  data = data_filtered_593bd084,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-56}
# 
result <- viz_stackedbar(
  data = data_filtered_577c6c25,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### Middle


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-57}
# 
result <- viz_stackedbar(
  data = data_filtered_51ea7279,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-58}
# 
result <- viz_stackedbar(
  data = data_filtered_cae4b485,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-59}
# 
result <- viz_stackedbar(
  data = data_filtered_ecf84d0e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-60}
# 
result <- viz_stackedbar(
  data = data_filtered_1c870641,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-61}
# 
result <- viz_stackedbar(
  data = data_filtered_57056314,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-62}
# 
result <- viz_stackedbar(
  data = data_filtered_eb413204,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-63}
# 
result <- viz_stackedbar(
  data = data_filtered_621f4df0,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


##### High


::: {.panel-tabset}

###### All Countries

```{r attitudes-towards-regulation-among-different-subgr-64}
# 
result <- viz_stackedbar(
  data = data_filtered_42f6fc86,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Netherlands

```{r attitudes-towards-regulation-among-different-subgr-65}
# 
result <- viz_stackedbar(
  data = data_filtered_a5527f6f,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Denmark

```{r attitudes-towards-regulation-among-different-subgr-66}
# 
result <- viz_stackedbar(
  data = data_filtered_cf3b699b,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### USA

```{r attitudes-towards-regulation-among-different-subgr-67}
# 
result <- viz_stackedbar(
  data = data_filtered_b2522cfd,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Brazil

```{r attitudes-towards-regulation-among-different-subgr-68}
# 
result <- viz_stackedbar(
  data = data_filtered_339bde9d,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### South Africa

```{r attitudes-towards-regulation-among-different-subgr-69}
# 
result <- viz_stackedbar(
  data = data_filtered_46a4019a,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


###### Japan

```{r attitudes-towards-regulation-among-different-subgr-70}
# 
result <- viz_stackedbar(
  data = data_filtered_82c5bf0e,
  title = "",
  x_vars = c("Q10_developers_are_responsible", "Q10_free_companies", "Q10_government_decides", "Q10_involve_civil_society", "Q10_only_regulate_high_risk", "Q10_right_to_complain"),
  x_var_labels = c("The developers of AI should make sure that the technology is safe to use and respects the rights of users.", "AI should not be regulated, so that companies are free to develop AI without interference from government regulations.", "The government should determine when AI is safe to use.", "Developers of AI should involve users or groups, like civil society and consumer organisations in the design of AI.", "Only the riskiest systems with high risks for human rights, health, safety or the planet should be regulated, because too much regulation is bad for innovation.", "Users should have a right to complain when their rights and interests are not respected."),
  stack_order = c("Strongly agree", "Agree", "Neither agree, nor disagree", "Disagree", "Strongly disagree"),
  color_palette = c("#4575b4", "#91bfdb", "#ffffbf", "#fc8d59", "#d73027"),
  stacked_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::


:::

