---
title: "Authenticity Rankings"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_small_30obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Load custom highcharter charts

hc_obj_1 <- readRDS('hc_obj_1.rds')

```


To measure what individuals consider authentic journalistic content, we asked them to rank the following statements according from 1 (*most authentic*) to 5 (*least authentic*).

***Reading example***:

*In each of the six countries, people said that journalistic content that expresses a writer’s character, beliefs or personality is considered the most authentic journalistic content.*


<div style='height: 2rem;'></div>


```{r}
#| echo: false

hc_obj_1
```

