---
title: "GenAI use"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_6961obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_7d7cd613 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(!is.na(country))
data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_e4cbba6b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender != "Other")
data_filtered_5384598e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands" & gender != "Other")
data_filtered_0d2b385d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark" & gender != "Other")
data_filtered_64c41e20 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA" & gender != "Other")
data_filtered_4587f0fd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil" & gender != "Other")
data_filtered_9f1f2013 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa" & gender != "Other")
data_filtered_0db57f63 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan" & gender != "Other")

```


To measure how often, if at all, participants use generative AI tools, we asked them: *In a typical week, how often do you use generative Artificial Intelligence (AI) applications like ChatGPT, Claude or DeepSeek?*


<div style='height: 2rem;'></div>

## GenAI Use across countries


::: {.panel-tabset}

### All Countries

```{r genai-use-across-countries}
# 
result <- viz_bar(
  data = data_filtered_7d7cd613,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Netherlands

```{r genai-use-across-countries-2}
# 
result <- viz_bar(
  data = data_filtered_03566455,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r genai-use-across-countries-3}
# 
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r genai-use-across-countries-4}
# 
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r genai-use-across-countries-5}
# 
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r genai-use-across-countries-6}
# 
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r genai-use-across-countries-7}
# 
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## GenAI Use among Different Subgroups


::: {.panel-tabset}

### By Age Group


::: {.panel-tabset}

##### All Countries

```{r genai-use-among-different-subgroups-by-age-group}
# 
result <- viz_bar(
  data = data,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r genai-use-among-different-subgroups-by-age-group-2}
# 
result <- viz_bar(
  data = data_filtered_03566455,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r genai-use-among-different-subgroups-by-age-group-3}
# 
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r genai-use-among-different-subgroups-by-age-group-4}
# 
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r genai-use-among-different-subgroups-by-age-group-5}
# 
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r genai-use-among-different-subgroups-by-age-group-6}
# 
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r genai-use-among-different-subgroups-by-age-group-7}
# 
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "age_cat",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


### By Gender


::: {.panel-tabset}

##### All Countries

```{r genai-use-among-different-subgroups-by-gender}
# 
result <- viz_bar(
  data = data_filtered_e4cbba6b,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r genai-use-among-different-subgroups-by-gender-2}
# 
result <- viz_bar(
  data = data_filtered_5384598e,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r genai-use-among-different-subgroups-by-gender-3}
# 
result <- viz_bar(
  data = data_filtered_0d2b385d,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r genai-use-among-different-subgroups-by-gender-4}
# 
result <- viz_bar(
  data = data_filtered_64c41e20,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r genai-use-among-different-subgroups-by-gender-5}
# 
result <- viz_bar(
  data = data_filtered_4587f0fd,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r genai-use-among-different-subgroups-by-gender-6}
# 
result <- viz_bar(
  data = data_filtered_9f1f2013,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r genai-use-among-different-subgroups-by-gender-7}
# 
result <- viz_bar(
  data = data_filtered_0db57f63,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "gender",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


### By Education


::: {.panel-tabset}

##### All Countries

```{r genai-use-among-different-subgroups-by-education}
# 
result <- viz_bar(
  data = data,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r genai-use-among-different-subgroups-by-education-2}
# 
result <- viz_bar(
  data = data_filtered_03566455,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r genai-use-among-different-subgroups-by-education-3}
# 
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r genai-use-among-different-subgroups-by-education-4}
# 
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r genai-use-among-different-subgroups-by-education-5}
# 
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r genai-use-among-different-subgroups-by-education-6}
# 
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r genai-use-among-different-subgroups-by-education-7}
# 
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "",
  x_var = "GenAI_use",
  bar_type = "percent",
  group_var = "education",
  x_label = "",
  y_label = "Percent (%)",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::

