---
title: "Journalistic Principles"
format: html
---

```{r, include=FALSE}
# Initialize dashboardr page configuration (CSS/JS for charts)
dashboardr:::.page_config()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load dashboardr (includes dplyr, highcharter as dependencies)
library(dashboardr)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_large_76571obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_7d7cd613 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(!is.na(country))
data_filtered_03566455 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands")
data_filtered_beb8a137 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark")
data_filtered_a1803a37 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA")
data_filtered_6dcfcc28 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil")
data_filtered_4bc4c9f5 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa")
data_filtered_0c062950 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan")
data_filtered_e4cbba6b <- dashboardr:::.convert_haven(data) %>% dplyr::filter(gender != "Other")
data_filtered_5384598e <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Netherlands" & gender != "Other")
data_filtered_0d2b385d <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Denmark" & gender != "Other")
data_filtered_64c41e20 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "USA" & gender != "Other")
data_filtered_4587f0fd <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Brazil" & gender != "Other")
data_filtered_9f1f2013 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "South Africa" & gender != "Other")
data_filtered_0db57f63 <- dashboardr:::.convert_haven(data) %>% dplyr::filter(country == "Japan" & gender != "Other")

```


To measure which journalistic principles should guide the use of AI in journalism, we asked our respondents to choose their top three out of 11 commonly named principles.

***Reading example***:

*37.9% of all respondents across countries chose “maintaining content quality” as one of their top three journalistic principles.*


<div style='height: 2rem;'></div>

## Journalistic Principles across countries


::: {.panel-tabset}

### All Countries

```{r journalistic-principles-across-countries}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_7d7cd613,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Human responsibility for content", "Political neutrality", "Preventing job replacement", "Protecting user privacy", "Accessibility of content", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  color_palette = c("#EDC948", "#4E79A7", "#E15759", "#FF9DA7", "#59A14F", "#B07AA1", "#9C755F", "#76B7B2", "#BAB0AC", "#F28E2B", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Netherlands

```{r journalistic-principles-across-countries-2}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_03566455,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Maintaining content quality", "Human responsibility for content", "Transparency about AI use", "Preventing job replacement", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Diversity of perspectives", "Avoiding discrimination", "Protecting intellectual property", "Environmental sustainability"),
  color_palette = c("#EDC948", "#E15759", "#4E79A7", "#59A14F", "#FF9DA7", "#B07AA1", "#9C755F", "#BAB0AC", "#76B7B2", "#F28E2B", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Denmark

```{r journalistic-principles-across-countries-3}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Human responsibility for content", "Maintaining content quality", "Transparency about AI use", "Political neutrality", "Preventing job replacement", "Accessibility of content", "Protecting user privacy", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  color_palette = c("#E15759", "#EDC948", "#4E79A7", "#FF9DA7", "#59A14F", "#9C755F", "#B07AA1", "#76B7B2", "#BAB0AC", "#F28E2B", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### USA

```{r journalistic-principles-across-countries-4}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Preventing job replacement", "Political neutrality", "Human responsibility for content", "Protecting user privacy", "Avoiding discrimination", "Accessibility of content", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  color_palette = c("#4E79A7", "#EDC948", "#59A14F", "#FF9DA7", "#E15759", "#B07AA1", "#76B7B2", "#9C755F", "#F28E2B", "#BAB0AC", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Brazil

```{r journalistic-principles-across-countries-5}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Human responsibility for content", "Preventing job replacement", "Protecting intellectual property", "Avoiding discrimination", "Diversity of perspectives", "Environmental sustainability"),
  color_palette = c("#4E79A7", "#EDC948", "#FF9DA7", "#B07AA1", "#9C755F", "#E15759", "#59A14F", "#F28E2B", "#76B7B2", "#BAB0AC", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### South Africa

```{r journalistic-principles-across-countries-6}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Protecting user privacy", "Human responsibility for content", "Preventing job replacement", "Accessibility of content", "Avoiding discrimination", "Political neutrality", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  color_palette = c("#4E79A7", "#EDC948", "#B07AA1", "#E15759", "#59A14F", "#9C755F", "#76B7B2", "#FF9DA7", "#F28E2B", "#BAB0AC", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


### Japan

```{r journalistic-principles-across-countries-7}
# Journalistic Principles
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "Journalistic Principles",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Protecting user privacy", "Political neutrality", "Avoiding discrimination", "Diversity of perspectives", "Human responsibility for content", "Accessibility of content", "Protecting intellectual property", "Preventing job replacement", "Environmental sustainability"),
  color_palette = c("#EDC948", "#4E79A7", "#B07AA1", "#FF9DA7", "#76B7B2", "#BAB0AC", "#E15759", "#9C755F", "#F28E2B", "#59A14F", "#499894"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::

## Journalistic Principles among Different Subgroups


::: {.panel-tabset}

### By Age Group


::: {.panel-tabset}

##### All Countries

```{r journalistic-principles-among-different-subgroups}
# 
result <- viz_bar(
  data = data,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Human responsibility for content", "Political neutrality", "Preventing job replacement", "Protecting user privacy", "Accessibility of content", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r journalistic-principles-among-different-subgroups-2}
# 
result <- viz_bar(
  data = data_filtered_03566455,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Maintaining content quality", "Human responsibility for content", "Transparency about AI use", "Preventing job replacement", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Diversity of perspectives", "Avoiding discrimination", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r journalistic-principles-among-different-subgroups-3}
# 
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Human responsibility for content", "Maintaining content quality", "Transparency about AI use", "Political neutrality", "Preventing job replacement", "Accessibility of content", "Protecting user privacy", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r journalistic-principles-among-different-subgroups-4}
# 
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Preventing job replacement", "Political neutrality", "Human responsibility for content", "Protecting user privacy", "Avoiding discrimination", "Accessibility of content", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r journalistic-principles-among-different-subgroups-5}
# 
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Human responsibility for content", "Preventing job replacement", "Protecting intellectual property", "Avoiding discrimination", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r journalistic-principles-among-different-subgroups-6}
# 
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Protecting user privacy", "Human responsibility for content", "Preventing job replacement", "Accessibility of content", "Avoiding discrimination", "Political neutrality", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r journalistic-principles-among-different-subgroups-7}
# 
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "age_cat",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Protecting user privacy", "Political neutrality", "Avoiding discrimination", "Diversity of perspectives", "Human responsibility for content", "Accessibility of content", "Protecting intellectual property", "Preventing job replacement", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


### By Gender


::: {.panel-tabset}

##### All Countries

```{r journalistic-principles-among-different-subgroups-8}
# 
result <- viz_bar(
  data = data_filtered_e4cbba6b,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Human responsibility for content", "Political neutrality", "Preventing job replacement", "Protecting user privacy", "Accessibility of content", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r journalistic-principles-among-different-subgroups-9}
# 
result <- viz_bar(
  data = data_filtered_5384598e,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Maintaining content quality", "Human responsibility for content", "Transparency about AI use", "Preventing job replacement", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Diversity of perspectives", "Avoiding discrimination", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r journalistic-principles-among-different-subgroups-10}
# 
result <- viz_bar(
  data = data_filtered_0d2b385d,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Human responsibility for content", "Maintaining content quality", "Transparency about AI use", "Political neutrality", "Preventing job replacement", "Accessibility of content", "Protecting user privacy", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r journalistic-principles-among-different-subgroups-11}
# 
result <- viz_bar(
  data = data_filtered_64c41e20,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Preventing job replacement", "Political neutrality", "Human responsibility for content", "Protecting user privacy", "Avoiding discrimination", "Accessibility of content", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r journalistic-principles-among-different-subgroups-12}
# 
result <- viz_bar(
  data = data_filtered_4587f0fd,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Human responsibility for content", "Preventing job replacement", "Protecting intellectual property", "Avoiding discrimination", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r journalistic-principles-among-different-subgroups-13}
# 
result <- viz_bar(
  data = data_filtered_9f1f2013,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Protecting user privacy", "Human responsibility for content", "Preventing job replacement", "Accessibility of content", "Avoiding discrimination", "Political neutrality", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r journalistic-principles-among-different-subgroups-14}
# 
result <- viz_bar(
  data = data_filtered_0db57f63,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "gender",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Protecting user privacy", "Political neutrality", "Avoiding discrimination", "Diversity of perspectives", "Human responsibility for content", "Accessibility of content", "Protecting intellectual property", "Preventing job replacement", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


### By Education


::: {.panel-tabset}

##### All Countries

```{r journalistic-principles-among-different-subgroups-15}
# 
result <- viz_bar(
  data = data,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Human responsibility for content", "Political neutrality", "Preventing job replacement", "Protecting user privacy", "Accessibility of content", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Netherlands

```{r journalistic-principles-among-different-subgroups-16}
# 
result <- viz_bar(
  data = data_filtered_03566455,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Maintaining content quality", "Human responsibility for content", "Transparency about AI use", "Preventing job replacement", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Diversity of perspectives", "Avoiding discrimination", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Denmark

```{r journalistic-principles-among-different-subgroups-17}
# 
result <- viz_bar(
  data = data_filtered_beb8a137,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Human responsibility for content", "Maintaining content quality", "Transparency about AI use", "Political neutrality", "Preventing job replacement", "Accessibility of content", "Protecting user privacy", "Avoiding discrimination", "Diversity of perspectives", "Protecting intellectual property", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### USA

```{r journalistic-principles-among-different-subgroups-18}
# 
result <- viz_bar(
  data = data_filtered_a1803a37,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Preventing job replacement", "Political neutrality", "Human responsibility for content", "Protecting user privacy", "Avoiding discrimination", "Accessibility of content", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Brazil

```{r journalistic-principles-among-different-subgroups-19}
# 
result <- viz_bar(
  data = data_filtered_6dcfcc28,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Political neutrality", "Protecting user privacy", "Accessibility of content", "Human responsibility for content", "Preventing job replacement", "Protecting intellectual property", "Avoiding discrimination", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### South Africa

```{r journalistic-principles-among-different-subgroups-20}
# 
result <- viz_bar(
  data = data_filtered_4bc4c9f5,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Transparency about AI use", "Maintaining content quality", "Protecting user privacy", "Human responsibility for content", "Preventing job replacement", "Accessibility of content", "Avoiding discrimination", "Political neutrality", "Protecting intellectual property", "Diversity of perspectives", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


##### Japan

```{r journalistic-principles-among-different-subgroups-21}
# 
result <- viz_bar(
  data = data_filtered_0c062950,
  title = "",
  x_var = "item",
  value_var = "mentioned",
  bar_type = "mean",
  group_var = "education",
  x_order = c("Maintaining content quality", "Transparency about AI use", "Protecting user privacy", "Political neutrality", "Avoiding discrimination", "Diversity of perspectives", "Human responsibility for content", "Accessibility of content", "Protecting intellectual property", "Preventing job replacement", "Environmental sustainability"),
  horizontal = TRUE,
  x_label = "",
  y_label = "% mentioned",
  tooltip_suffix = "%",
  subtitle = "Education levels: low (hasn't finished highschool), middle (finished highschool but not university), high (finished university)"
)

# Extract cross-tab data BEFORE wrapping (wrapping strips attributes)
cross_tab_data <- attr(result, 'cross_tab_data')
cross_tab_config <- attr(result, 'cross_tab_config')
cross_tab_id <- attr(result, 'cross_tab_id')

# Embed cross-tab data for client-side filtering
if (!is.null(cross_tab_data)) {
  cross_tab_json <- jsonlite::toJSON(cross_tab_data, dataframe = 'rows')
  config_json <- jsonlite::toJSON(cross_tab_config, auto_unbox = TRUE)
  script_tag <- htmltools::tags$script(
    htmltools::HTML(paste0(
      'window.dashboardrCrossTab = window.dashboardrCrossTab || {};',
      'window.dashboardrCrossTab["', cross_tab_id, '"] = {',
      'data: ', cross_tab_json, ',',
      'config: ', config_json,
      '};'
    ))
  )
  result <- htmltools::tagList(script_tag, result)
}

result
```


:::


:::

